Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-18 summary.tex
appendix

\documentclass[main.tex]{subfiles}
\begin{document}
\begin{center}
	\large \textbf{Summary}
\end{center}
This dissertation is a literature study, investigating the Finite Element Analysis of multidimensional and simplified beam and plate models. The Timoshenko beam and Reissner-Mindlin plate theories are popular theories used in mathematics and engineering. An example of ongoing research using these theories is the study of suspension bridges. The articles \cite{McK99}, \cite{BOC20} are examples of mathematical studies while \cite{SV86} follows an engineering approach.\\

>>>>

\documentclass[main.tex]{subfiles}
\begin{document}

\textbf{Title} Finite element analysis of multi-dimensional and simplified models for beams and plates

\textbf{Name} Rudi du Toit

\textbf{Supervisor} Prof NFJ van Rensburg

\textbf{Department} Mathematics and Applied Mathematics

\textbf{Degree} MSc Applied Mathematics

\begin{center}
	\large \textbf{Summary}
\end{center}
This dissertation is a literature study, investigating the Finite Element Analysis of multidimensional and simplified beam and plate models. The Timoshenko beam and Reissner-Mindlin plate theories are popular theories used in mathematics and engineering. An example of ongoing research using these theories is the study of suspension bridges. The articles \cite{Mck99}, \cite{BOC20} are examples of mathematical studies while \cite{SV86} follows an engineering approach.\\
